\large Neural and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2024-02-28 docs/papers/sto/so.tex
WIP draft abstract

We optimize the spatial resolution of cosmological particle-mesh (PM)
simulations by sharpening the PM force with first neural networks and
then symbolic regression, taking symmetry and dimensional analysis in
consideration.

We combine differentiable simulation, deep learning, [decision tree
(feature selection)], and symbolic regression to extract the final
kernel applicable to all other cosmological simulation code.

>>>>

We optimize the spatial resolution of cosmological particle-mesh (PM)
simulations by sharpening the PM force with first neural networks (NNs)
and then symbolic regression (SR), taking symmetry and dimensional
analysis in consideration.
We embed deep NNs in the differentiable cosmological $N$-body
simulation, and training them to learn for the force kernel.
We fit the trained NNs with SR to extract an analytic kernel for better
interpretability and physical insights, which is also applicable to all
other cosmological PM simulation code.
